### 2015-07-21 rscripts/data_review.Rmd
gif movie

```{r, echo=FALSE, include=FALSE}
req.packages <- c("data.table", "ggplot2", "reshape2", "grid", "scales")
need.pkgs <- req.packages[!sapply(req.packages, require, character.only = T)]
if (length(need.pkgs) != 0) install.packages(need.pkgs, dependencies = T)
```

@@

```{r, echo=F}
duration_breaks <- censor.dt[,quantile(logout-login, probs=(1:2)/3)]
daily_login_breaks <- censor.dt[,.N,by=list(location_id, login_day)][,quantile(N,probs=(1:2)/3)] ## TODO zeros?
# for 90 day window
#  for extant locations
#   - what percent of active days fall in each login category?
#   - what percent of logins fall in each login category?
```

>>>>

```{r, echo=FALSE, include=FALSE}
req.packages <- c("data.table", "ggplot2", "reshape2", "grid", "scales", "animation")
need.pkgs <- req.packages[!sapply(req.packages, require, character.only = T)]
if (length(need.pkgs) != 0) install.packages(need.pkgs, dependencies = T)
```

@@

```{r, echo=F}
duration_breaks <- censor.dt[,quantile(logout-login, probs=(1:2)/3)]
daily_login_breaks <- censor.dt[,.N,by=list(location_id, login_day)][,quantile(N,probs=(1:2)/3)] ## TODO zeros?

offset <- window <- 90; slide <- 30 ## TODO: go by actual months

divy <- function(dt) dt[,
  list( # use temp vars to calc actuals
    low = low/high,
    mid = (mid-low)/high,
    high = (high-mid)/high
  ),
  keyby=location_id
]

cross_group <- function(timeslice, duration_breaks, daily_login_breaks) {
  duration_group.dt <- divy(timeslice[,
    list( # initial pass to get temp variables
      low = sum((logout - login) <= duration_breaks[1]),
      mid = sum((logout - login) <= duration_breaks[2]),
      high = .N
    ), 
    keyby=location_id
  ])
  login_group.dt <- divy(timeslice[, 
    list(count = .N), 
    by=list(login_day, location_id)
  ][,
    list( # initial pass to get temp variables
      low = sum(count <= daily_login_breaks[1]),
      mid = sum(count <= daily_login_breaks[2]),
      high = .N
    ), 
    keyby=location_id
  ])
  cross_data.dt <- merge(
    melt(
      duration_group.dt, id.vars = "location_id",
      value.name="membership", variable.name="group"
    ),
    melt(
      login_group.dt, id.vars = "location_id",
      value.name="membership", variable.name="group"
    ),
    by = "location_id",
    allow.cartesian = T,
    suffixes = c(".duration",".login")
  )
}
# censor.dt[,max(login_day)]

base_scale_x <- scale_x_discrete("location",
  limits = 1:censor.dt[,max(unique(location_id))])
base_scale_y <- scale_y_continuous("membership", limits=c(0,1))

base_plot <- ggplot() + theme_bw() +
    facet_grid(group.duration ~ group.login, labeller = function(var, val) {
      paste0(val,ifelse(var == "group.duration"," duration"," logins"))
    }) +
    aes(x=location_id, y=membership.duration*membership.login,
        color = membership.duration*membership.login - membership.duration.prev*membership.login.prev) +
    base_scale_x + base_scale_y + theme(
      axis.text.x = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    ) +
    scale_color_gradient("change in membership", limits = c(-1,1), low="red", high="blue", na.value = "black")

prev.dt <- cross_group(censor.dt[offset <= login_day & login_day < (offset+window)], duration_breaks, daily_login_breaks)
saveGIF(for (start in seq(offset+slide, censor.dt[,max(login_day)]-window, by=slide)) {
  timeslice <- censor.dt[start <= login_day & login_day < (start+window)]
  cross_data.dt <- cross_group(timeslice, duration_breaks, daily_login_breaks)
  plotting.dt <- merge(cross_data.dt, prev.dt, by=c("location_id", "group.duration", "group.login"), all=T, suffixes = c("",".prev"))
  print(base_plot +
    geom_point(data = plotting.dt[!is.na(membership.duration.prev)], na.rm = TRUE) +
    geom_point(data = plotting.dt[is.na(membership.duration.prev)]) +
    geom_point(
      data=plotting.dt[
        is.na(membership.duration),
        list(
          membership.duration=membership.duration.prev,
          membership.login=membership.login.prev
        ),
        by=list(group.duration, group.login, location_id)
      ], color="black", shape = 1)
  )
  prev.dt <- cross_data.dt
})
```
